A Simple Minibatch Acceptance Test for MCMC

### 2016-05-19 nips_2016.tex
OK Haoyu and I are calling it a night for now.

In this experiment, we apply about minibatch MH testing with SGHMC (Stochastic Gradient Hamiltonian
Monte Carlo~\cite{sghmc_2014}) proposer to sample the parameter instances from a fully connected
neural network. We use Higgs data set from University of California Irvine. It is a classification
problem to distinguish between a signal process which produces Higgs bosons and a background process
which does not. We build a 4 layers neural network to tackle this problem. The first layer is a
input layer, the last layer is a softmax layer, the intermediate layers are linear followed by
Sigmoid, norm, dropout, starting and ending with linear operation.

We choose the Adaptive Gradient Descent method~\cite{adapGrad} as the comparison baseline. Since
the frequencies of the features are quite different, we use the same strategy in the Adaptive
Gradient to rescale the gradient before apply SGHMC. We implement our system within the open-source
BIDMach project~\cite{canny2013bidmach}.

Figure~\ref{fig:nnet_fig} illustrates our experiment results.

\begin{figure}[t]
    \centering
    \includegraphics[width=1\linewidth]{exp3}
    \caption{TODO This will hopefully show results for neural networks on BIDMach.}
    \label{fig:nnet_fig}
    %\vspace{-10pt}
\end{figure}

>>>>

In this experiment, we apply our minibatch MH test with a Stochastic Gradient Hamiltonian
Monte Carlo (SGHMC)~\cite{sghmc_2014} proposer to sample the parameter instances from a fully connected
neural network. We use the Higgs data set from the UCI dataset~\cite{Lichman:2013}. The network we
use for this binary classification problem has four layers and is fully connected. The first layer
is the input, the last layer is the softmax, and the intermediate layers apply the sigmoid
activation unit.  We also employ dropout and batch normalization~\cite{icml2015_ioffe15}.

For our comparison baseline, we train the same network architecture using the Adaptive Gradient
Descent method~\cite{adapGrad}. Since the frequencies of the features are quite different, we use
the same strategy in the Adaptive Gradient to rescale the gradient before apply SGHMC. We implement
our MH test and Adaptive Gradient in the open-source BIDMach project~\cite{canny2013bidmach}.

Figure~\ref{fig:nnet_fig} illustrates our experiment results and reveals that SGHMC with our
minibatch MH test achieves higher log likelihood than the baseline. By comparing SGHMC with and
without our minibatch MH test, we see that our MH test has limited benefit. Because we decrease the
step size quickly, the acceptance rate of SGHMC is already high, so there is little need to test.
% Daniel's note: Haoyu said he cannot increase the step size without it violating the variance
% condition.

\begin{figure}[t]
    \centering
    \includegraphics[width=1\linewidth]{exp3}
    \caption{Log likelihood versus number of passes for optimization of neural network.}
    \label{fig:nnet_fig}
    \vspace{-10pt}
\end{figure}
